Collaboratively exploring in an unknown environment under limited communication constraints is an essential and challenging task for a multi-robot system.
Robots in a team need to build a shared global map, tell their location within the map, and steer to the unexplored space.
Various Distributed Simultaneous Localization and Mapping (DSLAM) systems offer solutions to localize robots in communication constrained environments, where no external positioning signals and the communication between robots is limited.
However, current DSLAM systems rely on high-precision inter-robot place recognition methods. It is communication-costing to share the complicated feature for inter-robot place recognition and the sensor data for inter-robot relative pose estimation.
In the multi-robot exploration system, each robot's map has already been shared to build a global map.
Thus we use the grid map, instead of the feature and the sensor data, to do inter-robot place recognition and relative pose estimation to reduce data transmission.
Current DSLAM systems are also vulnerable to mistaken place recognition. Thus the robot trajectories need to overlay each other in an area to use the temporal or geometric information to improve the accuracy of place recognition.
However, current multi-robot exploration strategies are usually not stable, which means a big difference between different robots' exploration trajectories for the same space, resulting in a small overlay area.
In this paper, we propose a stable multi-robot exploration method that ensures the consistency of the trajectories when different robots exploring the same area and thus improves the accuracy of place recognition.